Interactively Visualizing Multivariate Market Segmentation Using the R Package Lionfish

### 2024-10-02 manuscript.tex
added abstract. minor addition to conclusion. marked proramming languages as such. italicize the k's of k means

%% an abstract and keywords
\Abstract{
Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum
Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum
Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum
Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum
Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum
Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum
Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum
Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum Lorem ipsum
}
\Keywords{interactive graphics, tourr, exploratory data analysis, \proglang{R}, \proglang{python}}
\Plainkeywords{keywords, comma-separated, non-capitalized,, R} %% without formatting
%% at least one keyword must be supplied

@@

While tour animations are best obtained within R using the tourr package~\citep{tourr}, it does not enable the interactivity required for example for a manual tour~\citep{laa2023new}. Interactive graphics are available when using Javascript, as implemented in the detourr package \citep{RJ-2023-052}. This allows to replay a recorded tour path with interactive graphics, and can also be linked with additional displays, but lacks capabilities for manual tours.

To integrate user interactions with the capabilities of the tourr package an active communication with the interface is required. For example, we may wish to explore the local neighbourhood of a projection selected by the user with a local tour animation provided by tourr, or we may want to optimize a guided tour path using groups identified via brushing.
Our solution is using Python for high-performance interactivity, through the packages \texttt{TKinter} \citep{lundh1999introduction}, \texttt{CustomTKinter} \citep{schimansky24}, and \texttt{matplotlib} \citep{Hunter:2007}, with integration to the tourr package \citep{tourr} via \texttt{reticulate} \citep{reticulate}, a framework that facilitates seamless interoperability between Python and R.

@@

The interface was implemented in the R package \texttt{lionfish} and offers a variety of linked interactive plot types, providing users with the flexibility to visualize their data from multiple perspectives. The ability to navigate through various projections of the displayed tours directly within a graphical user interface (GUI) enables users to explore different aspects of the dataset. Furthermore, users can initiate new tours directly from the interface. The GUI also supports interactive feature selection, allowing users to specify which subset of features should be visualized in the plots. Once users have identified interesting views or settings, \texttt{lionfish} allows them to save the displayed projections, subsets, and plots. This functionality ensures that analysis states can be preserved for further examination or reporting, making the package particularly useful for iterative analysis where findings may need to be revisited or shared with collaborators.

@@

The \texttt{Save projections and subsets} button can be used to save the current state of the analysis. These states can be recovered by using pressing the \texttt{Load projections and subsets} button. Additionally, users can initiate new tours directly from the sidebar. The options for new tour paths are: a local tour around the currently shown projection and guided tours that search for projections based on the holes- or the linear discriminant analysis (LDA) index. The holes index is sensitive to projections with few points in the center of the projections and the LDA index aims to maximize the distance between the centers of the selectet subsets. \textcolor{red}{XXX is this true? other options?} Additionally, all tour displays allow users to perform a manual tour; by right-clicking and dragging the arrowheads of projection axes, the projection is recalculated accordingly. This allows for manual exploration of the data.

@@

The majority of \texttt{lionfish} was written in Python \citep{python}, while the R \citep{R} side of the package handles setting up the Python environment within the interactive interface is being run, launching the interactive tour, and generating new tours when initiated through the interface. To incorporate the functionality of the \texttt{tourr} package without translating large portions of its code from R to Python, the \texttt{reticulate} package was used. This approach allows \texttt{lionfish} to automatically benefit from updates to \texttt{tourr}.

However, to reduce inefficiencies caused by cross-language communication and to simplify debugging, \texttt{tourr} functions were only accessed when necessary. Core functionalities, such as performing data transformations using projections, were implemented directly in Python. These transformations are based on well-established mathematical principles and are straightforward to replicate, ensuring they remain stable and efficient.

@@

The central component of the Python code is the \texttt{customTKinter} class \texttt{InteractiveTourInterface}. This class centrally stores attributes related to all plots, such as the dataset, sub-selections, feature selections, and other shared information. Plot-specific data is organized in dictionaries (the Python equivalent of named lists in R), including the display type, construction instructions, tour projections (only in case of tour displays), color schemes for the displayed data, and, where applicable, the selector and manual projection manipulation classes.

@@

In this example, while the intra-cluster fraction for cluster 1 and feature 1 is notably high at 0.9, the intra-feature fraction is comparatively low at 0.2. Applied to the subsequent analysis, this indicates that 90 \% of tourists in cluster 1 participated in activity 1, yet only 20 \% of all tourists who engaged in activity 1 were part of cluster 1. The majority of individuals participating in activity 1 were members of cluster 2. This discrepancy may be attributed to cluster 1 representing a relatively small group of tourists, characterized by a pronounced preference for activity 1 and a lack of interest in other activities.

@@

To gain further insight into the dataset a k-means clustering as described in \cite{leisch2018market} has been performed. Therefore, the function \texttt{stepcclust} of the R package \texttt{flexclust}\citep{flexclust} with $k=6$ and $nrep=20$ was used.

@@

We can now repeat the k-means clustering with \texttt{stepcclust} on the reduced dataset. Silhouette plots of both cluster solutions can be seen in Figure \ref{fig:silhouette_comparison}. By comparing both silhouette plots, we can see that the cluster solution with the reduced dataset results in a clustering of higher quality. Thus, we will continue with the analysis on the reduced dataset with the corresponding cluster solution. We can also see in Figure \ref{fig:silhouette_comparison}B that cluster 3 is of comparatively low quality. It is important to note that the silhouette scores were generally quite low, reflecting the lack of clearly separable clusters in the data. Consequently, there is no objectively correct or optimal solution. The primary aim of this analysis, therefore, is to gain insights into the data rather than to identify the optimal clustering configuration.

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{silhouette_comparison.png}
    \caption{Comparison of silhouette plots of two k-means cluster solutions of the Austrian vacation activities dataset with k=6. (A) shows the silhouette plot of the k-means solution of the full dataset and (B) the silhouette plot of the k-means solution of the dataset after manual feature selection. We can see that the cluster solution with the reduced dataset achieved better silhouette scores and that clusters 1 and 3 contain observations with negative silhouette scores.}
    \label{fig:silhouette_comparison}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_activ_cluster_highlights.png}
    \caption{Display of a projection of the Austrian vacation activities dataset with the six clusters of the k-means cluster solution highlighted in different colors. Projection axes with a norm < 0.1 have been blend out to reduce cluttering. The colors indicate which clusters the highlighted observations belong to with cluster 1 being blue (A), cluster 2 being orange (B), cluster 3 being green (C), cluster 4 being red (D), cluster 5 being violet (E) and cluster 6 being brown (F). Some datapoints appear to be highlighted always, which occurs due to overlap of many datapoints in one spot. We can see that the projection separates some clusters well, however also that there is considerable overlap of clusters 4, 5 and 6.}
    \label{fig:winter_activ_cluster_highlights}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_cl7_init.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the k-means solution of the Austrian vacation activities dataset. Projection axes with a norm < 0.1 have been blend out to reduce cluttering. Top left: 2D tour with the linear discriminant analysis projection pursuit index. Top right: heatmap with the intra-cluster fraction. Bottom left: 1D tour with the linear discriminant analysis projection pursuit index. Bottom right: mosaic plot. Tourists in both clusters 1 and 3 didn't participate in skiing a lot, but tourists in cluster 3 were much more interested in going to the pool, spa and health facilities compared to cluster 1.}
    \label{fig:winter_cl7_init}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_cl7_pre.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the k-means solution of the Austrian vacation activities dataset, with manually adjusted projections. Projection axes with a norm < 0.1 have been blend out to reduce cluttering. Top left: 2D tour with the linear discriminant analysis projection pursuit index. Top right: heatmap with the intra-cluster fraction. Bottom left: 1D tour with the linear discriminant analysis projection pursuit index. Bottom right: mosaic plot. Changing the projection axes of ``going to a spa'', ``museums'', ``sightseeing'' and ``using health facilities'' reveals the preferences and overlap of clusters 1 and 3.}
    \label{fig:winter_cl7_pre}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_cl7_post.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the k-means solution of the Austrian vacation activities dataset, after new subsets have been selected. Projection axes with a norm < 0.1 have been blend out to reduce cluttering. Top left: 2D tour with the linear discriminant analysis projection pursuit index. Top right: heatmap with the intra-cluster fraction. Bottom left: 1D tour with the linear discriminant analysis projection pursuit index. Bottom right: mosaic plot. We can see that now almost all museum goers are in the new manually selected subset 7 and what their preferences are compared to the other clusters.}
    \label{fig:winter_cl7_post}
\end{figure}

@@

At first, hierarchical clustering using Ward's method \citep{murtagh2014ward} and the Jaccard index was applied to the features. The resulting dendrogram is shown in Figure \ref{fig:aus_feature_clustering}. Based on this clustering, \( k = 15 \) clusters were identified, and generally, only one representative feature from each cluster was selected for further analysis. Clusters containing unpopular activities, such as ``Adventure'', which only had 42 participants, were discarded. The cluster containing popular features like ``Beach'', ``Swimming'', ``ScenicWalks'', ``Markets'', ``Sightseeing'', ``Friends'', ``Pubs'', ``BBQ'', ``Shopping'', ``Eating'', ``EatingHigh'', ``Movies'', and ``Relaxing'' was treated differently. Multiple features from this cluster were retained to preserve as much information as possible. After feature selection, the observations were reclustered using k-means with \( k = 15 \).

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{aus_heatmap.png}
    \caption{Heatmap of the intra cluster fraction (indicated by color) of the k-means solution with \( k = 6 \) and the reduced feature subset. We can observe that tourists in subsets 1, 2 and 6 all prefer to travel without their friends.}
    \label{fig:aus_heatmapg}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{aus_preselection.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the k-means solution of the Australian vacation activities dataset, with the projection axes of the feature ``Friends'' pointing into one direction and all the other ones into another one. Top left: 2D tour. Top right: 1D tour. Bottom left: Mosaic plot. Bottom right: Heatmap with the intra cluster fraction. We can see how the feature ``Friends'' and the general activity level (represented by the other projection axes pointing into one direction) separates the data.}
    \label{fig:aus_preselection}
\end{figure}

@@

Future developments in the software might include expanding the range of interactive features and providing additional visualization methods.  Because it is built on R and python, it would also be possible to integrate more closely with the machine learning algorithms, such as generating new cluster solutions directly from the GUI. For more complex shapes, containing concavities, or non-linear boundaries, implementation of sliced tours~\citep{Laa2020}, would be recommended.

@@

>>>>

%% an abstract and keywords
\Abstract{
Market segmentation presents a challenge in data science, particularly when dealing with high-dimensional data where regions of interest often overlap. In such cases, traditional feature selection and clustering algorithms can fall short in delivering both optimal and actionable solutions. The complexity of customer behavior, characterized by multiple and often overlapping traits, further complicates the identification of distinct market segments that can guide precise and targeted marketing strategies. Addressing these challenges requires a more nuanced and interactive approach to data exploration and analysis.

In this study, we analyzed two datasets derived from surveys conducted in Austria and Australia, where tourists reported on their vacation activities. These datasets serve as examples of the challenges posed by market segmentation. To address these, we developed and employed the \texttt{lionfish} \proglang{R} package, which facilitates interactive and dynamic exploration of clustering solutions. Unlike static approaches, \texttt{lionfish} allows users to refine clusters iteratively, focusing on aspects of the data most relevant to their specific analytical objectives. The package integrates tour algorithms through the \texttt{tourr} package, enabling advanced visualization of high-dimensional data, while \proglang{Python}-powered interactivity allows for manual adjustments and redefinition of cluster boundaries based on visual feedback.

By bridging the gap between automated algorithms and human intuition, \texttt{lionfish} enables analysts to surpass the limitations of traditional clustering methods. It offers a flexible, user-driven approach that reveals deeper insights into complex market behaviors, facilitating more effective segmentation and ultimately improving strategic decision-making.
}
\Keywords{interactive graphics, tourr, exploratory data analysis, \proglang{R}, \proglang{Python}}
\Plainkeywords{interactive graphics, tourr, exploratory data analysis, R, python} %% without formatting
%% at least one keyword must be supplied

@@

While tour animations are best obtained within \proglang{R} using the tourr package~\citep{tourr}, it does not enable the interactivity required for example for a manual tour~\citep{laa2023new}. Interactive graphics are available when using Javascript, as implemented in the detourr package \citep{RJ-2023-052}. This allows to replay a recorded tour path with interactive graphics, and can also be linked with additional displays, but lacks capabilities for manual tours.

To integrate user interactions with the capabilities of the tourr package an active communication with the interface is required. For example, we may wish to explore the local neighbourhood of a projection selected by the user with a local tour animation provided by tourr, or we may want to optimize a guided tour path using groups identified via brushing.
Our solution is using \proglang{Python} for high-performance interactivity, through the packages \texttt{TKinter} \citep{lundh1999introduction}, \texttt{CustomTKinter} \citep{schimansky24}, and \texttt{matplotlib} \citep{Hunter:2007}, with integration to the tourr package \citep{tourr} via \texttt{reticulate} \citep{reticulate}, a framework that facilitates seamless interoperability between \proglang{Python} and \proglang{R}.

@@

The interface was implemented in the \proglang{R} package \texttt{lionfish} and offers a variety of linked interactive plot types, providing users with the flexibility to visualize their data from multiple perspectives. The ability to navigate through various projections of the displayed tours directly within a graphical user interface (GUI) enables users to explore different aspects of the dataset. Furthermore, users can initiate new tours directly from the interface. The GUI also supports interactive feature selection, allowing users to specify which subset of features should be visualized in the plots. Once users have identified interesting views or settings, \texttt{lionfish} allows them to save the displayed projections, subsets, and plots. This functionality ensures that analysis states can be preserved for further examination or reporting, making the package particularly useful for iterative analysis where findings may need to be revisited or shared with collaborators.

@@

The \texttt{Save projections and subsets} button can be used to save the current state of the analysis. These states can be recovered by using pressing the \texttt{Load projections and subsets} button. Additionally, users can initiate new tours directly from the sidebar. The options for new tour paths are: a local tour around the currently shown projection and guided tours that search for projections based on the holes- or the linear discriminant analysis (LDA) index. The holes index is sensitive to projections with few points in the center of the projections and the LDA index aims to maximize the distance between the centers of the selectet subsets. \citep{ggobi} \textcolor{red}{XXX is this true? other options?} Additionally, all tour displays allow users to perform a manual tour; by right-clicking and dragging the arrowheads of projection axes, the projection is recalculated accordingly. This allows for manual exploration of the data.

@@

The majority of \texttt{lionfish} was written in \proglang{Python} \citep{python}, while the \proglang{R} \citep{R} side of the package handles setting up the \proglang{Python} environment within the interactive interface is being run, launching the interactive tour, and generating new tours when initiated through the interface. To incorporate the functionality of the \texttt{tourr} package without translating large portions of its code from \proglang{R} to \proglang{Python}, the \texttt{reticulate} package was used. This approach allows \texttt{lionfish} to automatically benefit from updates to \texttt{tourr}.

However, to reduce inefficiencies caused by cross-language communication and to simplify debugging, \texttt{tourr} functions were only accessed when necessary. Core functionalities, such as performing data transformations using projections, were implemented directly in \proglang{Python}. These transformations are based on well-established mathematical principles and are straightforward to replicate, ensuring they remain stable and efficient.

@@

The central component of the \proglang{Python} code is the \texttt{customTKinter} class \texttt{InteractiveTourInterface}. This class centrally stores attributes related to all plots, such as the dataset, sub-selections, feature selections, and other shared information. Plot-specific data is organized in dictionaries (the \proglang{Python} equivalent of named lists in \proglang{R}), including the display type, construction instructions, tour projections (only in case of tour displays), color schemes for the displayed data, and, where applicable, the selector and manual projection manipulation classes.

@@

In this example, while the intra-cluster fraction for cluster 1 and feature 1 is notably high at 0.9, the intra-feature fraction is comparatively low at 0.2. Applied to the subsequent analysis, this indicates that 90\% of tourists in cluster 1 participated in activity 1, yet only 20\% of all tourists who engaged in activity 1 were part of cluster 1. The majority of individuals participating in activity 1 were members of cluster 2. This discrepancy may be attributed to cluster 1 representing a relatively small group of tourists, characterized by a pronounced preference for activity 1 and a lack of interest in other activities.

@@

To gain further insight into the dataset a $k$-means clustering as described in \cite{leisch2018market} has been performed. Therefore, the function \texttt{stepcclust} of the \proglang{R} package \texttt{flexclust}\citep{flexclust} with $k=6$ and $nrep=20$ was used.

@@

We can now repeat the $k$-means clustering with \texttt{stepcclust} on the reduced dataset. Silhouette plots of both cluster solutions can be seen in Figure \ref{fig:silhouette_comparison}. By comparing both silhouette plots, we can see that the cluster solution with the reduced dataset results in a clustering of higher quality. Thus, we will continue with the analysis on the reduced dataset with the corresponding cluster solution. We can also see in Figure \ref{fig:silhouette_comparison}B that cluster 3 is of comparatively low quality. It is important to note that the silhouette scores were generally quite low, reflecting the lack of clearly separable clusters in the data. Consequently, there is no objectively correct or optimal solution. The primary aim of this analysis, therefore, is to gain insights into the data rather than to identify the optimal clustering configuration.

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{silhouette_comparison.png}
    \caption{Comparison of silhouette plots of two $k$-means cluster solutions of the Austrian vacation activities dataset with $k$=6. (A) shows the silhouette plot of the $k$-means solution of the full dataset and (B) the silhouette plot of the $k$-means solution of the dataset after manual feature selection. We can see that the cluster solution with the reduced dataset achieved better silhouette scores and that clusters 1 and 3 contain observations with negative silhouette scores.}
    \label{fig:silhouette_comparison}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_activ_cluster_highlights.png}
    \caption{Display of a projection of the Austrian vacation activities dataset with the six clusters of the $k$-means cluster solution highlighted in different colors. Projection axes with a norm < 0.1 have been blend out to reduce cluttering. The colors indicate which clusters the highlighted observations belong to with cluster 1 being blue (A), cluster 2 being orange (B), cluster 3 being green (C), cluster 4 being red (D), cluster 5 being violet (E) and cluster 6 being brown (F). Some datapoints appear to be highlighted always, which occurs due to overlap of many datapoints in one spot. We can see that the projection separates some clusters well, however also that there is considerable overlap of clusters 4, 5 and 6.}
    \label{fig:winter_activ_cluster_highlights}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_cl7_init.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the $k$-means solution of the Austrian vacation activities dataset. Projection axes with a norm < 0.1 have been blend out to reduce cluttering. Top left: 2D tour with the linear discriminant analysis projection pursuit index. Top right: heatmap with the intra-cluster fraction. Bottom left: 1D tour with the linear discriminant analysis projection pursuit index. Bottom right: mosaic plot. Tourists in both clusters 1 and 3 didn't participate in skiing a lot, but tourists in cluster 3 were much more interested in going to the pool, spa and health facilities compared to cluster 1.}
    \label{fig:winter_cl7_init}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_cl7_pre.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the $k$-means solution of the Austrian vacation activities dataset, with manually adjusted projections. Projection axes with a norm < 0.1 have been blend out to reduce cluttering. Top left: 2D tour with the linear discriminant analysis projection pursuit index. Top right: heatmap with the intra-cluster fraction. Bottom left: 1D tour with the linear discriminant analysis projection pursuit index. Bottom right: mosaic plot. Changing the projection axes of ``going to a spa'', ``museums'', ``sightseeing'' and ``using health facilities'' reveals the preferences and overlap of clusters 1 and 3.}
    \label{fig:winter_cl7_pre}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{winter_cl7_post.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the $k$-means solution of the Austrian vacation activities dataset, after new subsets have been selected. Projection axes with a norm < 0.1 have been blend out to reduce cluttering. Top left: 2D tour with the linear discriminant analysis projection pursuit index. Top right: heatmap with the intra-cluster fraction. Bottom left: 1D tour with the linear discriminant analysis projection pursuit index. Bottom right: mosaic plot. We can see that now almost all museum goers are in the new manually selected subset 7 and what their preferences are compared to the other clusters.}
    \label{fig:winter_cl7_post}
\end{figure}

@@

At first, hierarchical clustering using Ward's method \citep{murtagh2014ward} and the Jaccard index was applied to the features. The resulting dendrogram is shown in Figure \ref{fig:aus_feature_clustering}. Based on this clustering, \( k = 15 \) clusters were identified, and generally, only one representative feature from each cluster was selected for further analysis. Clusters containing unpopular activities, such as ``Adventure'', which only had 42 participants, were discarded. The cluster containing popular features like ``Beach'', ``Swimming'', ``ScenicWalks'', ``Markets'', ``Sightseeing'', ``Friends'', ``Pubs'', ``BBQ'', ``Shopping'', ``Eating'', ``EatingHigh'', ``Movies'', and ``Relaxing'' was treated differently. Multiple features from this cluster were retained to preserve as much information as possible. After feature selection, the observations were reclustered using $k$-means with \( k = 15 \).

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{aus_heatmap.png}
    \caption{Heatmap of the intra cluster fraction (indicated by color) of the $k$-means solution with \( k = 6 \) and the reduced feature subset. We can observe that tourists in subsets 1, 2 and 6 all prefer to travel without their friends.}
    \label{fig:aus_heatmapg}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{aus_preselection.png}
    \caption{Interactive tour GUI loaded with multiple plots showing different aspects of the $k$-means solution of the Australian vacation activities dataset, with the projection axes of the feature ``Friends'' pointing into one direction and all the other ones into another one. Top left: 2D tour. Top right: 1D tour. Bottom left: Mosaic plot. Bottom right: Heatmap with the intra cluster fraction. We can see how the feature ``Friends'' and the general activity level (represented by the other projection axes pointing into one direction) separates the data.}
    \label{fig:aus_preselection}
\end{figure}

@@

Future developments in the software might include expanding the range of interactive features and providing additional visualization methods. Because it is built on \proglang{R} and \proglang{Python}, it would also be possible to integrate more closely with the machine learning algorithms, such as generating new cluster solutions directly from the GUI. For more complex shapes, containing concavities, or non-linear boundaries, implementation of sliced tours~\citep{Laa2020}, would be recommended. Furthermore, it provides an additional demonstration of how \proglang{R} and \proglang{Python} can be integrated to harness the strengths of both programming languages.

@@

\section{Acknowledgements}~\label{acknowledgements}

The development of the \texttt{lionfish} package has been supported by the Google Summer of Code 2024 program.
